How Alignment Impact Language Learning Tasks? \\ A Visual Analytics Tool for Interpreting, Debugging, \\ and Tunning Text Entailment Model

### 2018-01-22 paper/paper_entailVis.tex
add comments

%% Paper title.
\title{How Attention Impact Language Learning Tasks? \\ A Visual Analytics Tool
for Interpreting, Debugging, \\ and Tunning Text Entailment Model}

@@

%% Abstract section.
\abstract{
In Natural Language Processs (NLP) research attention mechanism has gained a
strong following,

>>>>

%% Paper title.
\title{How Alignment Impact Language Learning Tasks? \\ A Visual Analytics Tool
for Interpreting, Debugging, \\ and Tunning Text Entailment Model}

@@

%% Abstract section.
% What are we doing in this paper
\abstract{
(What is the highlevel motivation)
Making sense and explaining the predictions made by deep neural networks
is not only essential for validating and improving the model, but also
becoming a necessity with increasing requirement for model accountabilty (e.g., for medical
application), as well as ethics concerns regarding the potential harm the
hidden biases learned by a black-box model~\cite{}.
%

(Limitation of the state-of-the arts)
Model independent explanations is useful to gain intuition,
but they lack an examination of the inner mechanism.
%

(What did we bring)
Recently attention mechanism~\cite{} has gained a strong following in
the Natural Language Processs (NLP) research.
